### 2014-11-10 docs/ms.Rmd
First draft of the conclusions finished

Rhiannon L. Dalrymple^1,6^, Daniel W. A. Noble^2,6^, James C. O’Hanlon ^2,6^, Kate D. L. Umbers^3,4,6^, Thomas E. White^2,6^, Daniel B. Zurek^5,6^

@@

^6^ Authors contributed equally and are presented in alphabetical order

@@

Our objective in this paper was not to point to single studies and lay blame, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross taxa comparisons. We hope our critical evaluation of recent litearture has highlighted a need for more careful reporting of methological reporting of how colour was measured, but also how it was analysed and can guide how research is communicated improving on the transparency and reproducibility of colour-based science. We belive that part of the issue is simply that researchers seldom have clear insight and guidance on what might be important aspects of their analysis and methods to be reported and we hope our paper will help estbalish more uniform reporting guidelines.

>>>>

Thomas E. White^2,6^, Rhiannon L. Dalrymple^1,6^, Daniel W. A. Noble^2,6^, James C. O’Hanlon ^2,6^, Daniel B. Zurek^5,6^, Kate D. L. Umbers^3,4,6^

@@

^6^ Authors contributed equally and are presented in random order

@@

Our review of recent colour literarure highlights some major reporting gaps that will hinder the reproducibility of studies quantifying colour signals. While we recognize that journals have space limitations and that work may reference previous methological and analytical details, we strongly beleive that studies can do a much better job reporting details which are essential to the transparency and reproducibility of their work. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investiagted expliclty stated. While all criteria are important some deserve special attanetion. In particular we found that colour scientists could do a much better job reporting light sources, number of pixel and spectra averaged used for analysis and the type of standards used. More improtantly, the distance and angle should be standard reporting for all studies using spectrophotomtry. These all have important consequences on downstream analysis and the reproducibility of colour signal quantification. As we all know, a picture can say 1000 words and we recommend the incoperation of spectral reflectance curves were possible as it provides insight on the colour signal, which is visually appealing and easy to understand by most readers. Surprisingly, we found that only `r round(fig, digits = 2)`% of studies using spectral reflectance data had an explicit figure in their paper showing these curves. Visual models were regularly used to analyse spectral data, something we welcome. However, there were many important aspects of the analysis that were seldom reported, inclding the type of quantum catch used, whether photoreceptor adaptation was accounted for and the type of neural noise used in receptor noise models. Photoreceptor densities should also be reported where possible even if using standard avian photorecptor densities.

In conclusion, our objective in this paper was not to point to single studies and lay blame, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross taxa comparisons. Indeed, even in our own work (e.g. Umbers et al. 2013) we have failed to report important details, which in resptrospec can lead to confusiion about how such data was collected and analysed. Nontheless, our critisim of reporting is meant to be constructive and is not to say that studies lacking improtant details are not excellent works, but it is only through critical appraisal and colleageal discussion that we can identify these gaps and constructively contribute to the growth of our field. Such assessments are particlularly important in an age where accountability, transparency and reproducibility of are utmost importance. We hope our critical evaluation of recent litearture has highlighted a need for more careful reporting of how colour signals have been measured and analysed. We beleive that part of the issue is simply that researchers seldom have clear guidelines to follow when undertaking research and miss what might be important aspects of their methods and analysis that need to be reported. We therefore hope that our paper will help estbalish more uniform reporting guidelines in the literature so that we can continue an exciting era of colour signal research in the life sciences.
